A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-17 mt-marathon.2013/PBML_article.tex
merge
made some changes to the description of joshua's decoding algorithm

\institute{label1}{University of Edinburgh}
\institute{label2}{Center for Language and Speech Processing, Johns Hopkins University}
\institute{label3}{Carnegie Mellon University}

@@

        \FORALL {LM state s}
          \IF {state s of hypothesis a != state s for hypothesis b}
	    \RETURN not equal
	 \ENDIF
        \ENDFOR
        \RETURN equal

\end{algorithmic}
\caption{Comparing Hypothesis States (old framework)}
\label{algo:CompareHypoStates}
\end{figure}

@@

\subsection{cdec and Joshua}
cdec and Joshua both have modern feature function frameworks similar to the Moses new framework. cdec has no distinction between stateful and stateless features; stateless features have zero size states.

@@

\subsection{cdec and Joshua}
In contrast to Moses which uses a one-pass search strategy, cdec and Joshua uses a multi-pass search strategy. That is, for each input sentence, all feature functions are evaluated when a hypothesis is created in Moses.

In cdec and Joshua, each pass creates a hypergraph that is used as the input for the next pass. Both decoders evaluates stateless feature functions in the first pass, followed by stateful feature functions in the second. Neither decoder partially evaluate stateful feature functions, as done in Moses.

@@

The results from the three decoders are comparable, given the same formalism and model data, and adjusting for scaling differences and constants. Figure~\ref{fig:model} shows the comparison of model scores and BLEU scores for a hierarchical model. Moses and cdec are roughly comparable in terms of speed. Also, Moses and cdec converges to roughly the same model scores, while Joshua makes more search errors, leading to lower BLEU scores.

@@

>>>>

\institute{label1}{University of Edinburgh}
\institute{label2}{Human Language Technology Center of Excellence, Johns Hopkins University}
\institute{label3}{Carnegie Mellon University}

@@

\begin{figure} [h!]
\small 
\begin{algorithmic}
\REQUIRE hypothesis $a$, hypothesis b
       \IF {coverage of a != coverage of b }
         \RETURN not equal
       \ENDIF

        \FORALL {LM state s}
          \IF {state s of hypothesis a != state s for hypothesis b}
            \RETURN not equal
          \ENDIF
        \ENDFOR
        \RETURN equal
\end{algorithmic}
\caption{Comparing Hypothesis States (old framework)}
\label{algo:CompareHypoStates}
\end{figure}

@@

\subsection{cdec and Joshua}
cdec and Joshua both have modern feature function frameworks similar to the Moses new
framework. Both of them have no distinction between stateful and stateless features; stateless
features have zero size states.

@@

\subsection{Joshua}

Joshua's decoding algorithm is an implementation of CKY+ \cite{chappelier1998generalized}. It
supports decoding with arbitrary synchronous CFG productions, imposing no limits on the rank of
rules or on the intermingling of terminals and nonterminals.

Joshua makes only a single CKY pass over the source language sentence; it does not build a
``stateless'' hypergraph (or --LM forest, in the language of \citet{chiang2007hierarchical}). To
enable this, Joshua interleaves the extension of partially-constructed rules with the application of
complete rules while building the hypergraph, depicted here with pseudocode:

\begin{figure} [h!]
\small 
\begin{algorithmic}
  \FORALL {spans $(i,j)$ in bottom-up order}
    \STATE {extend incomplete rules seeking the terminal at $(j-1,j)$}
    \FORALL {split points $k$}
      \STATE {extend incomplete rules over $(i,k)$ seeking a nonterminal $N$ such that chart item $(N,k,j)$ exists in the hypergraph}
    \ENDFOR
    \STATE {construct new hypergraph node by applying cube pruning to all completed rules over $(i,j)$}
  \ENDFOR
\end{algorithmic}
\caption{Interweaving of partially-completed and completed rules in Joshua.}
\label{algorithm:joshua}
\end{figure}

The chart containing partially-completed rules is called the \emph{dot chart}, and no pruning is
applied to it; rule features are computed only when complete rules are applied.

The efficiency gained from this interleaving allows Joshua to decode with SCFGs with rich
nonterminal sets \cite{galley2004whats,zollmann2006syntax}, although the time and memory
requirements increase dramatically. Incorporating feature scores into the dot chart for more
efficient decoding with SCFGs with rich nonterminal sets is a direction of interest.

\subsection{cdec}
In contrast to Moses and Joshua which use a one-pass search strategy, cdec uses a multi-pass search strategy. That is, for each input sentence, all feature functions are evaluated when a hypothesis is created in Moses.

In cdec, each pass creates a hypergraph that is used as the input for the next pass. cdec evaluates stateless feature functions in the first pass, followed by stateful feature functions in the second. Neither decoder partially evaluate stateful feature functions, as done in Moses.

@@

The results from the three decoders are comparable, given the same formalism and model data, and adjusting for scaling differences and constants.

@@

\subsection{Head-to-head}

Figure~\ref{fig:model} shows the comparison of model scores and BLEU scores for a hierarchical model. Moses and cdec are roughly comparable in terms of speed. Also, Moses and cdec converges to roughly the same model scores, while Joshua makes more search errors, leading to lower BLEU scores.
